---
title: "feature-based-queueing"
author: "Simrita Singh"
date: "2/16/2023"
output: html_document
---

## Loading the header file and the cost functions

```{r cars}
source("../utils/header.R")
source("../utils/cost_functions.R")
```

```{r}
library(triangulr)
```
# Taking two types
```{r}
costs=c(4,1)
p1=0.2
p2=0.8
lamda=c(p1,p2)
rho=c(0.2,0.6)
service=c(lamda[1]/rho[1],lamda[2]/rho[2])
```
## The densities of the two types
```{r}
  f_1=function(x){
  val=dtri(x, min = 0.5, max = 1, mode = 1, log = FALSE)
  return(val)
  }
 f_2=function(x){
  val=dtri(x, min = 0, max = 0.5, mode = 0, log = FALSE)
  return(val)
 }
 f_1=Vectorize(f_1)
 f_2=Vectorize(f_2)
 x_sample=runif(1000)
 density1=f_1(x_sample)
 density2=f_2(x_sample)
```


```{r}
plot(density1~x_sample)+
  points(density2~x_sample,col="blue")
```
```{r}
pmat_beta=function(beta){
  f11 <- function(x){(1/(1+exp(-beta[1]*x-beta[2])))*f_1(x)}
  f12 <- function(x){(1/(1+exp(beta[1]*x+beta[2])))*f_1(x)}
  f21 <- function(x){(1/(1+exp(-beta[1]*x-beta[2])))*f_2(x)}
  f22 <- function(x){(1/(1+exp(beta[1]*x+beta[2])))*f_2(x)}
  p11=integrate(f11, lower = 0, upper = 1)$value
  p12=integrate(f12, lower = 0, upper = 1)$value
  p21=integrate(f21, lower = 0, upper = 1)$value
  p22=integrate(f22, lower = 0, upper = 1)$value
  return(matrix(c(p11,p12,p21,p22),nrow=2,ncol=2,byrow=TRUE))
}
costs_beta=function(beta){
  pmat=pmat_beta(beta)
  return(as.numeric(net_cost_priority(pmat,c(1,2),lamda,service,costs)))
}
```




```{r}
opt=optim(par=c(10,0),fn=costs_beta)
pmat_beta(opt$par)
opt$value
#t(c(p1,p2))%*%pmat_beta(opt$par)
```

```{r}
net_cost_2(as.matrix(c(1,1)),lamda,service,costs)
```

```{r}
  f_1=function(x){
  val=dtri(x, min = 0, max = 1, mode = 1, log = FALSE)
  return(val)
  }
 f_2=function(x){
  val=dtri(x, min = 0, max = 1, mode = 0, log = FALSE)
  return(val)
 }
 f_1=Vectorize(f_1)
 f_2=Vectorize(f_2)
 x_sample=runif(1000)
 density1=f_1(x_sample)
 density2=f_2(x_sample)
```

```{r}
plot(density1~x_sample)+
points(density2~x_sample,col="blue")
```

```{r}
pmat_beta=function(beta){
  f11 <- function(x){(1/(1+exp(-beta[1]*x-beta[2])))*f_1(x)}
  f12 <- function(x){(1/(1+exp(beta[1]*x+beta[2])))*f_1(x)}
  f21 <- function(x){(1/(1+exp(-beta[1]*x-beta[2])))*f_2(x)}
  f22 <- function(x){(1/(1+exp(beta[1]*x+beta[2])))*f_2(x)}
  p11=integrate(f11, lower = 0, upper = 1)$value
  p12=integrate(f12, lower = 0, upper = 1)$value
  p21=integrate(f21, lower = 0, upper = 1)$value
  p22=integrate(f22, lower = 0, upper = 1)$value
  return(matrix(c(p11,p12,p21,p22),nrow=2,ncol=2,byrow=TRUE))
}
costs_beta=function(beta){
  pmat=pmat_beta(beta)
  return(as.numeric(net_cost_priority(pmat,c(1,2),lamda,service,costs)))
}
```




```{r}
opt=optim(par=c(0,0),fn=costs_beta)
pmat_beta(opt$par)
opt$value
#t(c(p1,p2))%*%pmat_beta(opt$par)
```



```{r}
net_cost_2(as.matrix(c(1,1)),lamda,service,costs)
```




```{r}
  f_1=function(x){
  val=dtri(x, min = 0, max = 1, mode = 0.6, log = FALSE)
  return(val)
  }
 f_2=function(x){
  val=dtri(x, min = 0, max = 1, mode = 0.4, log = FALSE)
  return(val)
 }
 f_1=Vectorize(f_1)
 f_2=Vectorize(f_2)
 x_sample=runif(1000)
 density1=f_1(x_sample)
 density2=f_2(x_sample)
```


```{r}
plot(density1~x_sample)+
points(density2~x_sample,col="blue")
```

```{r}
pmat_beta=function(beta){
  f11 <- function(x){(1/(1+exp(-beta[1]*x-beta[2])))*f_1(x)}
  f12 <- function(x){(1/(1+exp(beta[1]*x+beta[2])))*f_1(x)}
  f21 <- function(x){(1/(1+exp(-beta[1]*x-beta[2])))*f_2(x)}
  f22 <- function(x){(1/(1+exp(beta[1]*x+beta[2])))*f_2(x)}
  p11=integrate(f11, lower = 0, upper = 1)$value
  p12=integrate(f12, lower = 0, upper = 1)$value
  p21=integrate(f21, lower = 0, upper = 1)$value
  p22=integrate(f22, lower = 0, upper = 1)$value
  return(matrix(c(p11,p12,p21,p22),nrow=2,ncol=2,byrow=TRUE))
}
costs_beta=function(beta){
  pmat=pmat_beta(beta)
  return(as.numeric(net_cost_priority(pmat,c(1,2),lamda,service,costs)))
}
```




```{r}
opt=optim(par=c(0,0),fn=costs_beta)
pmat_beta(opt$par)
opt$value
#t(c(p1,p2))%*%pmat_beta(opt$par)
```


```{r}
net_cost_2(as.matrix(c(1,1)),lamda,service,costs)
```

## Hypothesis: For high feature-overlap, the waiting cost increases with feature-overlap
## Suppose the matrix is [], then for any classifier q(.), the waiting cost is increasing in the
##[],[1,0,0,1]
## if for any classifier, the waiting cost increases with the feature densities, then the optimal

c1mu1rho1(1-rho*P_11)+c2mu2rho2(1-rho*P_21)/(1-rho)(1-rho_1P11-\rho(P21))-
/
1-rho+rho*P_{21}


-1+rho-rho

```{r}

```




# As the feature overlap occurs, the relative gap between FIFO and multiple queues decreases. 
```{r}
costs=c(4,2,1)
p1=0.2
p2=0.3
p3=0.5
lamda=c(p1,p2,p3)
rho=c(0.1,0.2,0.5)
#service=c(sum(lamda)/rho,sum(lamda)/rho,sum(lamda)/rho)
service=c(lamda[1]/rho[1],lamda[2]/rho[2],lamda[3]/rho[3])
```

```{r}
pmat_beta=function(beta){
  f_1=function(x){
    if(as.numeric(x)>=0.5){
   val= 0.5*dtri(x, min = 0.5, max = 1, mode = 1, log = FALSE)
  }else{
   val= 0.5*dtri(x, min = 0, max = 0.5, mode = 0, log = FALSE)
  }
  return(val)
  }
  f_1=Vectorize(f_1)
  f11 <- function(x){(1/(1+exp(beta[1]*x)+exp(beta[1]*x+beta[2]*x)))*dtri(x, min = 0.5, max = 1, mode =1, log = FALSE)}
  f12 <- function(x){(1/(1+exp(-beta[1]*x)+exp(beta[2]*x)))*dtri(x, min = 0.5, max = 1, mode =1, log = FALSE)}
  f13 <- function(x){(1/(1+exp(-(beta[1]*x+beta[2]*x))+exp(-beta[2]*x)))*dtri(x, min = 0.5, max = 1, mode =1, log = FALSE)}
  f21 <- function(x){(1/(1+exp(beta[1]*x)+exp(beta[1]*x+beta[2]*x)))*dtri(x, min = 0, max = 0.5, mode =0, log = FALSE)}
  f22 <- function(x){(1/(1+exp(-beta[1]*x)+exp(beta[2]*x)))*dtri(x, min = 0, max = 0.5, mode =0, log = FALSE)}
  f23 <- function(x){(1/(1+exp(-(beta[1]*x+beta[2]*x))+exp(-beta[2]*x)))*dtri(x, min = 0, max =0.5, mode =0, log = FALSE)}
 # f31 <- function(x){(1/(1+exp(beta[1]*x)+exp(beta[1]*x+beta[2]*x)))*f_1(x)}
  #f32 <- function(x){(1/(1+exp(-beta[1]*x)+exp(beta[2]*x)))*f_1(x)}
  #f33 <- function(x){(1/(1+exp(-(beta[1]*x+beta[2]*x))+exp(-beta[2]*x)))*f_1(x)}
  f31 <- function(x){(1/(1+exp(beta[1]*x)+exp(beta[1]*x+beta[2]*x)))}
  f32 <- function(x){(1/(1+exp(-beta[1]*x)+exp(beta[2]*x)))}
  f33 <- function(x){(1/(1+exp(-(beta[1]*x+beta[2]*x))+exp(-beta[2]*x)))}
  p11=integrate(f11, lower = 0, upper = 1)$value
  p12=integrate(f12, lower = 0, upper = 1)$value
  p13=integrate(f13, lower = 0, upper = 1)$value
  p21=integrate(f21, lower = 0, upper = 1)$value
  p22=integrate(f22, lower = 0, upper = 1)$value
  p23=integrate(f23, lower = 0, upper = 1)$value
  p31=integrate(f31, lower = 0, upper = 1)$value
  p32=integrate(f32, lower = 0, upper = 1)$value
  p33=integrate(f33, lower = 0, upper = 1)$value
  return(matrix(c(p11,p12,p13,p21,p22,p23,p31,p32,p33),nrow=3,ncol=3,byrow=TRUE))
}
costs_beta=function(beta){
  pmat=pmat_beta(beta)
  return(as.numeric(net_cost_priority(pmat,c(1,2,3),lamda,service,costs)))
}
```

```{r}
opt=optim(par=c(-10,-10),fn=costs_beta)
pmat_beta(opt$par)
opt$value
t(c(p1,p2,p3))%*%pmat_beta(opt$par)
```



```{r}
mat2=cbind(pmat_beta(opt$par)[,1],pmat_beta(opt$par)[,2]+pmat_beta(opt$par)[,3])
mat2
as.numeric(net_cost_2(mat2,lamda,service,costs))
```



```{r}
pmat_beta_two=function(beta){
    f_1=function(x){
    if(as.numeric(x)>=0.5){
   val= 0.5*dtri(x, min = 0.5, max = 1, mode = 1, log = FALSE)
  }else{
   val= 0.5*dtri(x, min = 0, max = 0.5, mode = 0, log = FALSE)
  }
  return(val)
  }
  f_1=Vectorize(f_1)
  f11 <- function(x){(1/(1+exp(beta[1]*x)+exp(beta[1]*x+beta[2]*x)))*dtri(x, min = 0.5, max = 1, mode = 1, log = FALSE)}
  f12 <- function(x){((1/(1+exp(-beta[1]*x)+exp(beta[2]*x)))+(1/(1+exp(-(beta[1]*x+beta[2]*x))+exp(-beta[2]*x))))*dtri(x, min = 0.5, max = 1, mode = 1, log = FALSE)}
  f21 <- function(x){(1/(1+exp(beta[1]*x)+exp(beta[1]*x+beta[2]*x)))*dtri(x, min = 0, max = 0.5, mode = 0, log = FALSE)}
  f22 <- function(x){((1/(1+exp(-beta[1]*x)+exp(beta[2]*x)))+(1/(1+exp(-(beta[1]*x+beta[2]*x))+exp(-beta[2]*x))))*dtri(x, min = 0, max = 0.5, mode = 0, log = FALSE)}
  f31 <- function(x){(1/(1+exp(beta[1]*x)+exp(beta[1]*x+beta[2]*x)))}
  f32 <- function(x){((1/(1+exp(-beta[1]*x)+exp(beta[2]*x)))+(1/(1+exp(-(beta[1]*x+beta[2]*x))+exp(-beta[2]*x))))}
  p11=integrate(f11, lower = 0, upper = 1)$value
  p12=integrate(f12, lower = 0, upper = 1)$value
  p21=integrate(f21, lower = 0, upper = 1)$value
  p22=integrate(f22, lower = 0, upper = 1)$value
  p31=integrate(f31, lower = 0, upper = 1)$value
  p32=integrate(f32, lower = 0, upper = 1)$value
  return(matrix(c(p11,p12,p21,p22,p31,p32),nrow=3,ncol=2,byrow=TRUE))
}
costs_beta_two=function(beta){
  pmat=pmat_beta_two(beta)
  return(as.numeric(net_cost_2(pmat,lamda,service,costs)))
}
```

```{r}
opt2=optim(par=c(-10,-10),fn=costs_beta_two)
pmat_beta_two(opt2$par)
opt2$value
t(c(p1,p2,p3))%*%pmat_beta_two(opt2$par)
```


```{r}
t(c(p1,p2,p3))%*%pmat_beta_two(opt2$minimum)
```

```{r}
pmat_beta_two(opt2$minimum)
mat3=cbind(pmat_beta_two(opt2$minimum)[,1],0.5*pmat_beta_two(opt2$minimum)[,2],0.5*pmat_beta_two(opt2$minimum)[,2])
net_cost_2(mat3,lamda,service,costs)
```

