---
title: "optimal_classification_matrix_total_variation"
author: "Simrita Singh"
date: "7/18/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("../utils/header.R")
```

```{r}
source("../utils/cost_functions.R")
```

```{r}
sample_tv=1000
tv_13=runif(sample_tv)
tv_12=runif(sample_tv)*tv_13
tv_23=(tv_13-tv_12)+runif(sample_tv)*tv_12
```

```{r}
cost3=1
cost2=2
cost1=2+sample_tv*runif(sample_tv)
rho=runif(sample_tv)
p1=runif(sample_tv)
p2=runif(sample_tv)
p3=runif(sample_tv)
sum_p=p1+p2+p3
p1=p1/sum_p
p2=p2/sum_p
p3=p3/sum_p
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(rho,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```




```{r}
classification_matrix_ideal1=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(1,0),c(1-tv_12,tv_12),c(1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_ideal1=Vectorize(classification_matrix_ideal1, SIMPLIFY = FALSE)
classification_matrix_ideal2=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(1,0),c(1-tv_13+tv_23,tv_13-tv_23),c(1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_ideal2=Vectorize(classification_matrix_ideal2, SIMPLIFY = FALSE)
classification_matrix_ideal3=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(1,0),c(1,0),c(1-tv_23,tv_23))
  return(as.matrix(pmat))
  }
classification_matrix_ideal3=Vectorize(classification_matrix_ideal3, SIMPLIFY = FALSE)

```

```{r}
data_params<- data_params %>% mutate(pmat_ideal1=classification_matrix_ideal1(tv_13,tv_12,tv_23),
                                     pmat_ideal2=classification_matrix_ideal2(tv_13,tv_12,tv_23),
                                     pmat_ideal3=classification_matrix_ideal3(tv_13,tv_12,tv_23)
                                                      )
```


```{r}
head(data_params)
```

```{r}
net_cost_2_expanded<-function(ml_algo,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3){
den1=1-lambda1*ml_algo[1,1]/service1-lambda2*ml_algo[2,1]/service2-lambda3*ml_algo[3,1]/service3
den2=den1-lambda1*ml_algo[1,2]/service1-lambda2*ml_algo[2,2]/service2-lambda3*ml_algo[3,2]/service3
num1=cost1*lambda1*ml_algo[1,1]+cost2*lambda2*ml_algo[2,1]+cost3*lambda3*ml_algo[3,1]
num2=cost1*lambda1*ml_algo[1,2]+cost2*lambda2*ml_algo[2,2]+cost3*lambda3*ml_algo[3,2]
return((num1/den1+num2/(den1*den2))*(lambda1/(service1^2)+lambda2/(service2^2)+lambda3/(service3^2)))
}
net_cost_2_expanded=Vectorize(net_cost_2_expanded)
```

```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_ideal1=net_cost_2_expanded(pmat_ideal1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_ideal2=net_cost_2_expanded(pmat_ideal2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_ideal3=net_cost_2_expanded(pmat_ideal3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3)
)
                                   #cost_pmat_try=net_cost_2_try(pmat,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   #cost_pmat_ideal_try=net_cost_2_try(pmat_ideal,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   #cost_pmat_ideal2_try=net_cost_2_try(pmat_ideal2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3)                       #)
```


```{r}
nrow(data_params)
```


```{r}
data_params=data_params %>% filter(tv_13>=tv_12 & tv_13>=tv_23 & tv_12+tv_23>=tv_13)
nrow(data_params)
```


# Numerically testing which of the classification matrices can take the minimum value
```{r}

data_params = data_params %>% mutate(min_cost=pmin(cost_pmat_ideal1,cost_pmat_ideal2,cost_pmat_ideal3))
```

```{r}
which(data_params$min_cost==data_params$cost_pmat_ideal3)
```

```{r}
data_params[which(data_params$min_cost==data_params$cost_pmat_ideal3),]
```

```{r}
data_params[which(data_params$min_cost==data_params$cost_pmat_ideal3)[1],]$pmat_ideal3
```







```{r}
head(data_params)
```

















```{r}
data_viol = data_params_samples %>% filter(cost_pmat< min_cost, (pmat[[1]][1,3] < pmat[[1]][2,3]), (pmat[[1]][2,3]< pmat[[1]][3,3]), (pmat[[1]][1,3]> pmat[[1]][3,3]-tv_13), (pmat[[1]][2,3] > pmat[[1]][3,3]-tv_23), (pmat[[1]][1,3] > pmat[[1]][2,3]-tv_12 ))


data_viol = data_viol %>% mutate(flag13=(pmat[[1]][1,3] > pmat[[1]][3,3]-tv_13))

data_viol = data_viol %>% filter(flag13==TRUE)
data_viol[2,]$flag13
data_viol[2,]$pmat
data_viol[2,]$tv_13

data_viol = data_viol %>% mutate(flag23=(pmat[[1]][2,3] > pmat[[1]][3,3]-tv_23))

data_viol = data_viol %>% filter(flag23==TRUE)
data_viol[2,]$flag23
data_viol[2,]$pmat
data_viol[2,]$tv_23

data_viol = data_viol %>% mutate(flag12=(pmat[[1]][1,3] > pmat[[1]][2,3]-tv_12))

data_viol = data_viol %>% filter(flag12==TRUE)
data_viol[2,]$flag12
data_viol[2,]$pmat
data_viol[2,]$tv_13
data_viol[2,]$tv_12
data_viol[2,]$tv_23
```

```{r}
names(data_viol)
```
```{r}
class(data_viol)
```



```{r}
distinct(data_viol[,1:9])

```


```{r}
data_viol2=data_viol %>% group_by(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23,min_cost) %>% summarise(cost_pmat=min(cost_pmat)) %>% ungroup()

```

```{r}
dat=left_join(data_viol2,data_viol,by="cost_pmat")
```


```{r}
dat
```

```{r}
truths=vector()
for(i in 1:nrow(dat)){
  truths[i]=(dat[i,]$pmat[[1]][3,3]-dat[i,]$pmat[[1]][1,3]<dat[i,]$tv_13.x) *(dat[i,]$pmat[[1]][2,3]-dat[i,]$pmat[[1]][1,3]<dat[i,]$tv_12.x)*(dat[i,]$pmat[[1]][3,3]-dat[i,]$pmat[[1]][2,3]<dat[i,]$tv_23.x)
}
truths
```



```{r}
dat[1,]$pmat
dat[1,]$tv_13.x
dat[1,]$tv_12.x
dat[1,]$tv_23.x


```
```{r}
View(dat[8,])
```



```{r}

data1=data_params %>% filter(cost_pmat_ideal==min_cost) 
data2=data_params %>% filter(cost_pmat_ideal2==min_cost)
data3=data_params %>% filter(cost_pmat_ideal3==min_cost)
data4=data_params %>% filter(cost_pmat_ideal4==min_cost)
data5=data_params %>% filter(cost_pmat_ideal5==min_cost)
data6=data_params %>% filter(cost_pmat_ideal6==min_cost)
data7=data_params %>% filter(cost_pmat_ideal7==min_cost)
data8=data_params %>% filter(cost_pmat_ideal8==min_cost)
data9=data_params %>% filter(cost_pmat_ideal9==min_cost)
data10=data_params %>% filter(cost_pmat_ideal10==min_cost)
data11=data_params %>% filter(cost_pmat_ideal11==min_cost)
data12=data_params %>% filter(cost_pmat_ideal12==min_cost)
data13=data_params %>% filter(cost_pmat_ideal13==min_cost)
data14=data_params %>% filter(cost_optimal<min_cost)
nrow(data1)
nrow(data2)
nrow(data3)
nrow(data4)
nrow(data5)
nrow(data6)
nrow(data7)
nrow(data8)
nrow(data9)
nrow(data10)
nrow(data11)
nrow(data12)
nrow(data13)
nrow(data14)
```


```{r}
```


```{r}
data_params[1,]
```


```{r}
lambda1=data_params[1,]$lambda1
lambda2=data_params[1,]$lambda2
lambda3=data_params[1,]$lambda3
service1=data_params[1,]$service1
service2=data_params[1,]$service2
service3=data_params[1,]$service3
cost1=data_params[1,]$cost1
cost2=data_params[1,]$cost2
cost3==data_params[1,]$cost3
tv_13=data_params[1,]$tv_13
tv_12=data_params[1,]$tv_12
tv_23=data_params[1,]$tv_23
pmat_ideal=data_params[1,]$pmat_ideal[[1]]
```



```{r}
pmat_ideal
```

```{r}
net_cost_2(pmat_ideal,lamda = c(lambda1,lambda2,lambda3),service=c(service1,service2,service3),costs=c(cost1,cost2,cost3))
```


```{r}
net_cost_2_expanded(ml_algo,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3)
```




# Check if Matrix one is dominated by any matrix: it is not

```{r}
max(data_params$cost_pmat_ideal2-data_params$cost_pmat_ideal)
max(data_params$cost_pmat_ideal3-data_params$cost_pmat_ideal)
max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal)
max(data_params$cost_pmat_ideal5-data_params$cost_pmat_ideal)
max(data_params$cost_pmat_ideal6-data_params$cost_pmat_ideal)
max(data_params$cost_pmat_ideal7-data_params$cost_pmat_ideal)
```


# Check if Matrix two is dominated by any matrix : it is by matrix 1

```{r}
max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal2)
max(data_params$cost_pmat_ideal3-data_params$cost_pmat_ideal2)
max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal2)
max(data_params$cost_pmat_ideal5-data_params$cost_pmat_ideal2)
max(data_params$cost_pmat_ideal6-data_params$cost_pmat_ideal2)
max(data_params$cost_pmat_ideal7-data_params$cost_pmat_ideal2)
```


# Check if Matrix three is dominated by any matrix : : it is by matrix 5 and 6


```{r}
max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal3)
max(data_params$cost_pmat_ideal2-data_params$cost_pmat_ideal3)
max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal3)
max(data_params$cost_pmat_ideal5-data_params$cost_pmat_ideal3)
max(data_params$cost_pmat_ideal6-data_params$cost_pmat_ideal3)
```


# Check if Matrix four is dominated by any matrix : : it is not



```{r}
max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4)
max(data_params$cost_pmat_ideal2-data_params$cost_pmat_ideal4)
max(data_params$cost_pmat_ideal3-data_params$cost_pmat_ideal4)
max(data_params$cost_pmat_ideal5-data_params$cost_pmat_ideal4)
max(data_params$cost_pmat_ideal6-data_params$cost_pmat_ideal4)
max(data_params$cost_pmat_ideal7-data_params$cost_pmat_ideal4)
```


# Check if Matrix five is dominated by any matrix : : it is not

```{r}
max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal5)
max(data_params$cost_pmat_ideal2-data_params$cost_pmat_ideal5)
max(data_params$cost_pmat_ideal3-data_params$cost_pmat_ideal5)
max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal5)
max(data_params$cost_pmat_ideal6-data_params$cost_pmat_ideal5)
max(data_params$cost_pmat_ideal6-data_params$cost_pmat_ideal7)
```

# Check if Matrix six is dominated by any matrix : : it is not

```{r}
max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal6)
max(data_params$cost_pmat_ideal2-data_params$cost_pmat_ideal6)
max(data_params$cost_pmat_ideal3-data_params$cost_pmat_ideal6)
max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal6)
max(data_params$cost_pmat_ideal5-data_params$cost_pmat_ideal6)
max(data_params$cost_pmat_ideal7-data_params$cost_pmat_ideal6)
max(data_params$cost_pmat_ideal8-data_params$cost_pmat_ideal6)
max(data_params$cost_pmat_ideal9-data_params$cost_pmat_ideal6)
max(data_params$cost_pmat_ideal10-data_params$cost_pmat_ideal6)
```

# Check if Matrix 7 is dominated by any matrix : : it is not

```{r}
max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal7)
max(data_params$cost_pmat_ideal2-data_params$cost_pmat_ideal7)
max(data_params$cost_pmat_ideal3-data_params$cost_pmat_ideal7)
max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal7)
max(data_params$cost_pmat_ideal5-data_params$cost_pmat_ideal7)
max(data_params$cost_pmat_ideal6-data_params$cost_pmat_ideal7)
```




# Check if Matrix 8 is dominated by any matrix : : it is not

```{r}
max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal8)
max(data_params$cost_pmat_ideal2-data_params$cost_pmat_ideal8)
max(data_params$cost_pmat_ideal3-data_params$cost_pmat_ideal8)
max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal8)
max(data_params$cost_pmat_ideal5-data_params$cost_pmat_ideal8)
max(data_params$cost_pmat_ideal6-data_params$cost_pmat_ideal8)
max(data_params$cost_pmat_ideal7-data_params$cost_pmat_ideal8)
```

# Check if Matrix 9 is dominated by any matrix : : it is by mat 7 

```{r}
max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal9)
max(data_params$cost_pmat_ideal2-data_params$cost_pmat_ideal9)
max(data_params$cost_pmat_ideal3-data_params$cost_pmat_ideal9)
max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal9)
max(data_params$cost_pmat_ideal5-data_params$cost_pmat_ideal9)
max(data_params$cost_pmat_ideal6-data_params$cost_pmat_ideal9)
max(data_params$cost_pmat_ideal7-data_params$cost_pmat_ideal9)
max(data_params$cost_pmat_ideal8-data_params$cost_pmat_ideal9)
max(data_params$cost_pmat_ideal10-data_params$cost_pmat_ideal9)
```



# Check if Matrix 10 is dominated by any matrix : : it is by mat 7 and mat 9 

```{r}
max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal10)
max(data_params$cost_pmat_ideal2-data_params$cost_pmat_ideal10)
max(data_params$cost_pmat_ideal3-data_params$cost_pmat_ideal10)
max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal10)
max(data_params$cost_pmat_ideal5-data_params$cost_pmat_ideal10)
max(data_params$cost_pmat_ideal6-data_params$cost_pmat_ideal10)
max(data_params$cost_pmat_ideal7-data_params$cost_pmat_ideal10)
max(data_params$cost_pmat_ideal8-data_params$cost_pmat_ideal10)
max(data_params$cost_pmat_ideal9-data_params$cost_pmat_ideal10)
```







```{r}
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$pmat_ideal4
```
```{r}
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$pmat_ideal
```

```{r}
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$cost_pmat_ideal
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$cost_pmat_ideal4
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$cost1
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$cost2
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$cost3
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$tv_13
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$tv_23
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$tv_12
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$lambda1/data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$service1
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$lambda2/data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$service2
data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$lambda3/data_params[which.max(data_params$cost_pmat_ideal-data_params$cost_pmat_ideal4),]$service3
```




```{r}
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$pmat_ideal4
```


```{r}
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$pmat_ideal
```



```{r}
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$cost_pmat_ideal
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$cost_pmat_ideal4
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$cost1
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$cost2
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$cost3
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$tv_13
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$tv_23
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$tv_12
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$lambda1/data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$service1
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$lambda2/data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$service2
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$lambda3/data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$service3
```




# The above example shows 

```{r}
data_params[which.max(data_params$cost_pmat_ideal4-data_params$cost_pmat_ideal),]$pmat_ideal4
```




```{r}
net_cost_2_expanded<-function(ml_algo,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3){
den1=1-lambda1*ml_algo[1,1]/service1-lambda2*ml_algo[2,1]/service2-lambda3*ml_algo[3,1]/service3
den2=den1-lambda1*ml_algo[1,2]/service1-lambda2*ml_algo[2,2]/service2-lambda3*ml_algo[3,2]/service3
den3=den2-lambda1*ml_algo[1,3]/service1-lambda2*ml_algo[2,3]/service2-lambda3*ml_algo[3,3]/service3
num1=cost1*lambda1*ml_algo[1,1]+cost2*lambda2*ml_algo[2,1]+cost3*lambda3*ml_algo[3,1]
num2=cost1*lambda1*ml_algo[1,2]+cost2*lambda2*ml_algo[2,2]+cost3*lambda3*ml_algo[3,2]
num3=cost1*lambda1*ml_algo[1,3]+cost2*lambda2*ml_algo[2,3]+cost3*lambda3*ml_algo[3,3]
return((num1/den1+num2/(den1*den2)+num3/(den2*den3))*(lambda1/(service1^2)+lambda2/(service2^2)+lambda3/(service3^2)))
}
net_cost_2_expanded=Vectorize(net_cost_2_expanded)
```


```{r}
classification_matrix_1=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(1,0,0),c(1-tv_12,tv_12,0),c(1-tv_13,tv_13-tv_23,tv_23))
  return(as.matrix(pmat))
  }
classification_matrix_1=Vectorize(classification_matrix_1, SIMPLIFY = FALSE)



classification_matrix_2=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_23,1-tv_13,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_2=Vectorize(classification_matrix_2, SIMPLIFY = FALSE)


classification_matrix_3=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_13-tv_12,1-tv_13+tv_12,0),c(0,1-tv_23,tv_23))
  return(as.matrix(pmat))
  }
classification_matrix_3=Vectorize(classification_matrix_3, SIMPLIFY = FALSE)

classification_matrix_4=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_13-tv_12,1-2*tv_13+tv_12+tv_23,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_4=Vectorize(classification_matrix_4, SIMPLIFY = FALSE)



classification_matrix_5=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_12,1-tv_12,0),c(0,1-tv_13+tv_23,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_5=Vectorize(classification_matrix_5, SIMPLIFY = FALSE)
```

# Numerical Experiments case 1:

```{r}
tv_13=0.9
tv_12=0.6
tv_23=0.6
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.9
p1=0.2
p2=0.3
p3=0.5
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```





```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```


```{r}
ggsave("case1.pdf")
```



```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_1)[[1]] 
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_3)[[1]] 
```







# Numerical Experiments case 9:

```{r}
tv_13=0.9
tv_12=0.6
tv_23=0.6
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.9
p1=1/3
p2=1/3
p3=1/3
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```





```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )

```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```


```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_3)[[1]] 
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_1)[[1]] 
```

```{r}
ggsave("case9.pdf")
```




# Numerical Experiments case 2:

```{r}
tv_13=0.9
tv_12=0.85
tv_23=0.10
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.9
p1=0.2
p2=0.3
p3=0.5
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```




```{r}
classification_matrix_1=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(1,0,0),c(1-tv_12,tv_12,0),c(1-tv_13,tv_13-tv_23,tv_23))
  return(as.matrix(pmat))
  }
classification_matrix_1=Vectorize(classification_matrix_1, SIMPLIFY = FALSE)



classification_matrix_2=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_23,1-tv_13,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_2=Vectorize(classification_matrix_2, SIMPLIFY = FALSE)


classification_matrix_3=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_13-tv_12,1-tv_13+tv_12,0),c(0,1-tv_23,tv_23))
  return(as.matrix(pmat))
  }
classification_matrix_3=Vectorize(classification_matrix_3, SIMPLIFY = FALSE)

classification_matrix_4=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_13-tv_12,1-2*tv_13+tv_12+tv_23,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_4=Vectorize(classification_matrix_4, SIMPLIFY = FALSE)



classification_matrix_5=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_12,1-tv_12,0),c(0,1-tv_13+tv_23,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_5=Vectorize(classification_matrix_5, SIMPLIFY = FALSE)
```

```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```

```{r}
ggsave("case2.pdf")
```

```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_1)[[1]] 

```







# Numerical Experiments case 10:

```{r}
tv_13=0.9
tv_12=0.85
tv_23=0.10
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.9
p1=1/3
p2=1/3
p3=1/3
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```




```{r}
classification_matrix_1=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(1,0,0),c(1-tv_12,tv_12,0),c(1-tv_13,tv_13-tv_23,tv_23))
  return(as.matrix(pmat))
  }
classification_matrix_1=Vectorize(classification_matrix_1, SIMPLIFY = FALSE)



classification_matrix_2=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_23,1-tv_13,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_2=Vectorize(classification_matrix_2, SIMPLIFY = FALSE)


classification_matrix_3=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_13-tv_12,1-tv_13+tv_12,0),c(0,1-tv_23,tv_23))
  return(as.matrix(pmat))
  }
classification_matrix_3=Vectorize(classification_matrix_3, SIMPLIFY = FALSE)

classification_matrix_4=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_13-tv_12,1-2*tv_13+tv_12+tv_23,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_4=Vectorize(classification_matrix_4, SIMPLIFY = FALSE)



classification_matrix_5=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_12,1-tv_12,0),c(0,1-tv_13+tv_23,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_5=Vectorize(classification_matrix_5, SIMPLIFY = FALSE)
```

```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```


```{r}
ggsave("case10.pdf")
```

```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_1)[[1]] 

```




# Numerical Experiments case 3:

```{r}
tv_13=0.9
tv_12=0.10
tv_23=0.85
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.9
p1=0.2
p2=0.3
p3=0.5
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```


```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```

```{r}
ggsave("case3.pdf")
```




```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_1)[[1]] 
```


# Numerical Experiments case 11:

```{r}
tv_13=0.90
tv_12=0.10
tv_23=0.85
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.9
p1=1/3
p2=1/3
p3=1/3
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```


```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```

```{r}
ggsave("case11.pdf")
```




```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_1)[[1]] 
```















# Numerical Experiment Case 4
```{r}
tv_13=0.6
tv_12=0.35
tv_23=0.35
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.9
p1=0.2
p2=0.3
p3=0.5
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```


```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 
```

```{r}
ggsave("case4.pdf")
```


```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_3)[[1]] 
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_1)[[1]] 
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_4)[[1]] 
```




# Numerical Experiment Case 12
```{r}
tv_13=0.6
tv_12=0.35
tv_23=0.35
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.9
p1=1/3
p2=1/3
p3=1/3
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```


```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 
```

```{r}
ggsave("case12.pdf")
```


```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_1)[[1]] 
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_3)[[1]] 
```





























# Numerical Experiments case 5:

```{r}
tv_13=0.9
tv_12=0.6
tv_23=0.6
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.6
p1=0.2
p2=0.3
p3=0.5
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```




```{r}
classification_matrix_1=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(1,0,0),c(1-tv_12,tv_12,0),c(1-tv_13,tv_13-tv_23,tv_23))
  return(as.matrix(pmat))
  }
classification_matrix_1=Vectorize(classification_matrix_1, SIMPLIFY = FALSE)



classification_matrix_2=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_23,1-tv_13,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_2=Vectorize(classification_matrix_2, SIMPLIFY = FALSE)


classification_matrix_3=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_13-tv_12,1-tv_13+tv_12,0),c(0,1-tv_23,tv_23))
  return(as.matrix(pmat))
  }
classification_matrix_3=Vectorize(classification_matrix_3, SIMPLIFY = FALSE)

classification_matrix_4=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_13-tv_12,1-2*tv_13+tv_12+tv_23,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_4=Vectorize(classification_matrix_4, SIMPLIFY = FALSE)



classification_matrix_5=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_12,1-tv_12,0),c(0,1-tv_13+tv_23,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_5=Vectorize(classification_matrix_5, SIMPLIFY = FALSE)
```

```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```
```{r}
ggsave("case5.pdf")
```




```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_3)[[1]] 
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_4)[[1]] 
```



# Numerical Experiments case 13:

```{r}
tv_13=0.9
tv_12=0.6
tv_23=0.6
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.6
p1=1/3
p2=1/3
p3=1/3
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```



```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```
```{r}
ggsave("case13.pdf")
```




```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_3)[[1]] 
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_4)[[1]] 
```
# Numerical Experiments case 6:

```{r}
tv_13=0.9
tv_12=0.85
tv_23=0.10
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.6
p1=0.2
p2=0.3
p3=0.5
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```




```{r}
classification_matrix_1=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(1,0,0),c(1-tv_12,tv_12,0),c(1-tv_13,tv_13-tv_23,tv_23))
  return(as.matrix(pmat))
  }
classification_matrix_1=Vectorize(classification_matrix_1, SIMPLIFY = FALSE)



classification_matrix_2=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_23,1-tv_13,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_2=Vectorize(classification_matrix_2, SIMPLIFY = FALSE)


classification_matrix_3=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_13-tv_12,1-tv_13+tv_12,0),c(0,1-tv_23,tv_23))
  return(as.matrix(pmat))
  }
classification_matrix_3=Vectorize(classification_matrix_3, SIMPLIFY = FALSE)

classification_matrix_4=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_13,1-tv_13,0),c(tv_13-tv_12,1-2*tv_13+tv_12+tv_23,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_4=Vectorize(classification_matrix_4, SIMPLIFY = FALSE)



classification_matrix_5=function(tv_13,tv_12,tv_23){
  pmat=rbind(c(tv_12,1-tv_12,0),c(0,1-tv_13+tv_23,tv_13-tv_23),c(0,1-tv_13,tv_13))
  return(as.matrix(pmat))
  }
classification_matrix_5=Vectorize(classification_matrix_5, SIMPLIFY = FALSE)
```

```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```

```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_1)[[1]] 
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_5)[[1]] 
```


# Numerical Experiments case 7:

```{r}
tv_13=0.9
tv_12=0.10
tv_23=0.85
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.6
p1=0.2
p2=0.3
p3=0.5
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```







```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```

```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_4)[[1]] 
```


```{r}
tv_13=0.9
tv_12=0.85
tv_23=0.10
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.6
p1=1/3
p2=1/3
p3=1/3
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```





```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```


```{r}
ggsave("case14.pdf")
```



```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_1)[[1]] 
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_5)[[1]] 
```


# Numerical Experiments case 7:

```{r}
tv_13=0.9
tv_12=0.10
tv_23=0.85
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.6
p1=0.2
p2=0.3
p3=0.5
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```







```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```

```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_4)[[1]] 
```




# Numerical Experiments Case 15


```{r}
tv_13=0.9
tv_12=0.10
tv_23=0.85
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.6
p1=1/3
p2=1/3
p3=1/3
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```





```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```

```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_4)[[1]] 
```









# Numerical Experiments case 8:

```{r}
tv_13=0.6
tv_12=0.35
tv_23=0.35
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.6
p1=0.2
p2=0.3
p3=0.5
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```







```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```

```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_4)[[1]] 
```





# Numerical Experiments case 16:

```{r}
tv_13=0.6
tv_12=0.35
tv_23=0.35
cost3=1
cost2=2
cost1=seq(2.05,20,0.05)
rho=0.6
p1=1/3
p2=1/3
p3=1/3
lambda1=p1
lambda2=p2
lambda3=p3
service1=(lambda1+lambda2+lambda3)/rho
service2=(lambda1+lambda2+lambda3)/rho
service3=(lambda1+lambda2+lambda3)/rho
data_params=as.data.frame(cbind(lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3,tv_13,tv_12,tv_23))
```







```{r}
data_params <- data_params %>% mutate(pmat_1=classification_matrix_1(tv_13,tv_12,tv_23),
                                      pmat_2=classification_matrix_2(tv_13,tv_12,tv_23),
                                      pmat_3=classification_matrix_3(tv_13,tv_12,tv_23),
                                      pmat_4=classification_matrix_4(tv_13,tv_12,tv_23),
                                      pmat_5=classification_matrix_5(tv_13,tv_12,tv_23)
)
```



```{r}
data_params = data_params %>% mutate(
                                   cost_pmat_1=net_cost_2_expanded(pmat_1,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_2=net_cost_2_expanded(pmat_2,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_3=net_cost_2_expanded(pmat_3,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_4=net_cost_2_expanded(pmat_4,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3),
                                   cost_pmat_5=net_cost_2_expanded(pmat_5,lambda1,lambda2,lambda3,service1,service2,service3,cost1,cost2,cost3))
```



```{r}
data_params = data_params %>%
 pivot_longer(
   cols = c(cost_pmat_1,cost_pmat_2,cost_pmat_3,cost_pmat_4,cost_pmat_5),
   names_to = "Classification Matrix",
   values_to = "Average Waiting Cost",
 )
```


```{r}
ggplot(data = data_params,aes(x=cost1,y=`Average Waiting Cost`,color=`Classification Matrix`)) +
  geom_line() 

```

```{r}
t(as.matrix(rho*c(p1,p2,p3))) %*% as.matrix(data_params[1,]$pmat_4)[[1]] 
```