---
title: "optimal_classification_matrix_total_variation"
author: "Simrita Singh"
date: "7/18/2024"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
source("../utils/header.R")
```

```{r}
source("../utils/cost_functions.R")
```

```{r}
cost1=10
cost2=1
rho=0.7
p1=1/10
p2=9/10
lambda1=p1
lambda2=p2
service1=(lambda1+lambda2)/rho
service2=(lambda1+lambda2)/rho
lamda=c(lambda1,lambda2)
service=c(service1,service2)
costs=c(cost1,cost2)
ml_algo=rbind(c(1,0),c(0,1))
net_cost_2(ml_algo,lamda,service,costs)
```
```{r}
library(distr)
```
# sample size with 1000, 10000, 100000

```{r}
## Sampling types 1 and 2 given their probabilities p1 and p2
## Construct the distribution object.
myMix <- UnivarMixingDistribution(DiscreteDistribution(1), 
                                DiscreteDistribution(2),
                                  mixCoeff=c(p1,p2))
## ... and then a function for sampling random variates from it
rmyMix <- r(myMix)

## Sample a million random variates, and plot (part of) their histogram
x <- rmyMix(1000)
hist(x, col="grey", main="")
```
#Sampling features based on the sampled type
```{r}
sample_var=function(x){
  if(x==1){
    return(runif(1,0,3/2))
  }else if(x==2)
    {
    return(runif(1,-1,1))
  }
}
sample_var=Vectorize(sample_var)
```


```{r}
data=cbind(Type=x,X=sample_var(x))
data=as.data.frame(data)
hist(data$X, col="grey", main="")

```
```{r}
names(data)
```
```{r}
data$Type=as.numeric(sign(1-data$Type)+1)
```


```{r}
fit=glm(Type~X,data,family="binomial")
```

```{r}
#summary(fit)
```

```{r}
#plot(fit$fitted.values~data$X)
```

```{r}
classifier_predictions=fit$fitted.values
```


```{r}
estimated_cost_thresh=function(t){
  p11=sum(classifier_predictions*0.5*(1+sign(classifier_predictions-t)))/sum(classifier_predictions)
  p21=sum((1-classifier_predictions)*0.5*(1+sign(classifier_predictions-t)))/sum(1-classifier_predictions)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
estimated_cost_thresh=Vectorize(estimated_cost_thresh)
```



```{r}
thresholds=seq(0,1,0.001)
min(estimated_cost_thresh(thresholds))
t=thresholds[which.min(estimated_cost_thresh(thresholds))]
t
```


# The realized classification probabilities

```{r}
fit$coefficients
```




```{r}
fit$coefficients[1]
fit$coefficients[2]
```

```{r}
#(inv.logit(t)-fit$coefficients[1])
```


```{r}
(-log(1/t-1)-fit$coefficients[1])/fit$coefficients[2]
```

```{r}
qlogis(t)-fit$coefficients[1]
```


```{r}
x_c=(qlogis(t)-fit$coefficients[1])/fit$coefficients[2]
x_c
```

```{r}
p11=1-2*x_c/3
p21=1-(1+x_c)/2
p11
p21

```



```{r}
optim(0.5,estimated_cost_thresh,lower=0,upper=1,method = "Brent")
```

```{r}
log(thresholds[which.min(estimated_cost_thresh(thresholds))]/(1-thresholds[which.min(estimated_cost_thresh(thresholds))]))
```

```{r}
fit$coefficients
fit$coefficients[1]
fit$coefficients[2]
```



```{r}
(log(thresholds[which.min(estimated_cost_thresh(thresholds))]/(1-thresholds[which.min(estimated_cost_thresh(thresholds))]))-fit$coefficients[1])/fit$coefficients[2]
```


```{r}
estimated_cost_direct=function(par){
  beta_0=par[1]
  beta_1=par[2]
  p11=sum(data$Type*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(data$Type)
  p21=sum((1-data$Type)*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(1-data$Type)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}

```

```{r}
optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)
par=optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)$par
```

```{r}
x_c=-par[1]/par[2]
x_c
```

```{r}
p11=1-2*x_c/3
p21=1-(1+x_c)/2
p11
p21
```





### This assumes the type first is a logistic regression classifier obtained via MLE estimates

##### Running the Experiment 25 times ######


```{r}
source("../utils/cost_functions.R")
source("../utils/header.R")
library(distr)
```



```{r}
cost1=10
cost2=1
rho=0.7
p1=1/10
p2=9/10
lambda1=p1
lambda2=p2
service1=(lambda1+lambda2)/rho
service2=(lambda1+lambda2)/rho
service1
service2
ml_algo=rbind(c(1,0),c(0,1))
lamda=c(lambda1,lambda2)
service=c(service1,service2)
costs=c(cost1,cost2)
sample_size=10000
```

```{r}
pt_11=vector()
pt_21=vector()
pd_11=vector()
pd_21=vector()
wait_type1_typefirst <- vector()
wait_type2_typefirst <- vector()
wait_type1_direct <- vector()
wait_type2_direct <- vector()

for(i in 1:25){
myMix <- UnivarMixingDistribution(DiscreteDistribution(1), 
                                DiscreteDistribution(2),
                                  mixCoeff=c(p1,p2))
rmyMix <- r(myMix)
x <- rmyMix(sample_size)
#hist(x, col="grey", main="")
sample_var=function(x){
  if(x==1){
    return(runif(1,0,3/2))
  }else if(x==2)
    {
    return(runif(1,-1,1))
  }
}
sample_var=Vectorize(sample_var)
data=cbind(Type=x,X=sample_var(x))
data=as.data.frame(data)
data$Type=as.numeric(sign(1-data$Type)+1)
fit=glm(Type~X,data,family="binomial")
classifier_predictions=fit$fitted.values
estimated_cost_thresh=function(t){
  p11=sum(classifier_predictions*0.5*(1+sign(classifier_predictions-t)))/sum(classifier_predictions)
  p21=sum((1-classifier_predictions)*0.5*(1+sign(classifier_predictions-t)))/sum(1-classifier_predictions)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
estimated_cost_thresh=Vectorize(estimated_cost_thresh)
thresholds=seq(0,1,0.001)
min(estimated_cost_thresh(thresholds))
t=thresholds[which.min(estimated_cost_thresh(thresholds))]
x_c=(qlogis(t)-fit$coefficients[1])/fit$coefficients[2]
p11=1-2*x_c/3
p21=1-(1+x_c)/2
pt_11[i]=p11
pt_21[i]=p21
estimated_cost_direct=function(par){
  beta_0=par[1]
  beta_1=par[2]
  p11=sum(data$Type*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(data$Type)
  p21=sum((1-data$Type)*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(1-data$Type)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)
par=optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)$par
x_c=-par[1]/par[2]
p11=1-2*x_c/3
p21=1-(1+x_c)/2
pd_11[i]=p11
pd_21[i]=p21
# After getting ml_algo for type-first
ml_algo_tf=rbind(c(pt_11[i],1-pt_11[i]),c(pt_21[i],1-pt_21[i]))
priority_tf <- priority_sequence(ml_algo_tf, lamda, service, costs)
wait_type1_typefirst[i] <- wait_k(1,ml_algo_tf, lamda, service, costs, priority_tf)
wait_type2_typefirst[i] <- wait_k(2,ml_algo_tf, lamda, service, costs, priority_tf)
# After getting ml_algo for direct
ml_algo_direct=rbind(c(pd_11[i],1-pd_11[i]),c(pd_21[i],1-pd_21[i]))
priority_direct <- priority_sequence(ml_algo_direct, lamda, service, costs)
wait_type1_direct[i] <- wait_k(1, ml_algo_direct, lamda, service, costs, priority_direct)
wait_type2_direct[i] <- wait_k(2, ml_algo_direct, lamda, service, costs, priority_direct)
}
```


```{r}
# Type-First
mean_wait_t1_tf <- mean(wait_type1_typefirst)
se_wait_t1_tf   <- sd(wait_type1_typefirst) / sqrt(length(wait_type1_typefirst))
print(c(mean_wait_t1_tf,se_wait_t1_tf ))
mean_wait_t2_tf <- mean(wait_type2_typefirst)
se_wait_t2_tf   <- sd(wait_type2_typefirst) / sqrt(length(wait_type2_typefirst))
print(c(mean_wait_t2_tf,se_wait_t2_tf ))
# Direct
mean_wait_t1_d <- mean(wait_type1_direct)
se_wait_t1_d   <- sd(wait_type1_direct) / sqrt(length(wait_type1_direct))
print(c(mean_wait_t1_d,se_wait_t1_d ))
mean_wait_t2_d <- mean(wait_type2_direct)
se_wait_t2_d   <- sd(wait_type2_direct) / sqrt(length(wait_type2_direct))
print(c(mean_wait_t2_d,se_wait_t2_d ))
```





```{r}
# Type-First
mean_pt11 <- mean(pt_11)
se_pt11   <- sd(pt_11) / sqrt(length(pt_11))

mean_pt21 <- mean(pt_21)
se_pt21   <- sd(pt_21) / sqrt(length(pt_21))

# Direct
mean_pd11 <- mean(pd_11)
se_pd11   <- sd(pd_11) / sqrt(length(pd_11))

mean_pd21 <- mean(pd_21)
se_pd21   <- sd(pd_21) / sqrt(length(pd_21))

```

```{r}
install.packages("FNN")
library(FNN)
```

```{r}
# ---------------------------
# FIXED FULL R CODE
# ---------------------------

# Initialize result holder
results_all <- data.frame()

# Set constants
p1 <- 1/10
p2 <- 9/10
sample_size <- 10000
cost1 <- 10
cost2 <- 1
rho <- 0.7
lambda1 <- p1
lambda2 <- p2
lamda <- c(lambda1, lambda2)
service1 <- (lambda1 + lambda2) / rho
service2 <- (lambda1 + lambda2) / rho
service <- c(service1, service2)
costs <- c(cost1, cost2)

# Load required libraries
library(FNN)

# Helper functions
phi <- function(x, mu, sd) dnorm(x, mu, sd)
u <- function(x, a, b) {
  if (b - a <= 0) return(rep(0, length(x)))
  ifelse(x >= a & x <= b, 1 / (b - a), 0)
}

evaluate_classifier <- function(queue1, type, lamda, service, costs, method_name) {
  p11 <- replace_na(mean(queue1[type == 1] == 1),0)
  p21 <-replace_na(mean(queue1[type == 0] == 1),0)
  ml_algo <- matrix(c(p11, 1 - p11, p21, 1 - p21), nrow = 2, byrow = TRUE)
  priority <- priority_sequence(ml_algo, lamda, service, costs)
  wait1 <- p11*wait_k(1, ml_algo, lamda, service, costs, priority)+(1-p11)*wait_k(2, ml_algo, lamda, service, costs, priority)
  wait2 <- p21*wait_k(1, ml_algo, lamda, service, costs, priority)+(1-p21)*wait_k(2, ml_algo, lamda, service, costs, priority)

  return(data.frame(
    method = method_name,
    P11 = p11,
    P21 = p21,
    Wait1 = wait1,
    Wait2 = wait2
  ))
}

evaluate_type_first_classifier <- function(t1_vals, type, lamda, service, costs, method_name = "method") {
  if (all(is.na(t1_vals)) || length(t1_vals) == 0) {
    warning(paste("Skipping method:", method_name, "due to invalid t1_vals"))
    return(data.frame(method = method_name, P11 = NA, P21 = NA, Wait1 = NA, Wait2 = NA))
  }
 type=data$Type
  thresholds <- seq(0.000000001, 1, 0.001)
  # Here for estimating the cost function we don't use the actual type, instead we use the predicted type posteriors
  cost_fn <- function(t) {
    queue1 <- ifelse(t1_vals >= t, 1, 2)
    ml_algo <- matrix(0, 2, 2)
    ml_algo[1,1] <-sum(t1_vals*as.numeric(queue1 == 1))/sum(t1_vals)
    ml_algo[1,2] <- 1 - ml_algo[1,1]
    ml_algo[2,1] <- sum((1-t1_vals)*as.numeric(queue1 == 1))/sum(1-t1_vals)
    ml_algo[2,2] <- 1 - ml_algo[2,1]
    net_cost_2(ml_algo, lamda, service, costs)
  }

  costs_vec <- suppressWarnings(Vectorize(cost_fn)(thresholds))
  if (all(is.infinite(costs_vec))) {
    warning(paste("All costs are Inf for method:", method_name))
    return(data.frame(method = method_name, P11 = NA, P21 = NA, Wait1 = NA, Wait2 = NA))
  }

  t_opt <- thresholds[which.min(costs_vec)]
  queue1 <- ifelse(t1_vals >= t_opt, 1, 2)
  evaluate_classifier(queue1, type, lamda, service, costs, method_name)
}

get_knn_probs <- function(test_x, train_x, train_y, k) {
  neighbors <- FNN::get.knnx(data = matrix(train_x), query = matrix(test_x), k = k)
  apply(neighbors$nn.index, 1, function(idx) mean(train_y[idx] == 1))
}

# Main loop
set.seed(1200)
for (i in c(1)) {
  n1 <- round(sample_size * p1)
  n2 <- sample_size - n1
  x <- c(rep(1, n1), rep(2, n2))
  sample_var <- Vectorize(function(t) if (t == 1) runif(1, 0, 3/2) else runif(1, -1, 1))
  data <- data.frame(Type = as.numeric(sign(1 - x) + 1), X = sample_var(x))

  # 1. MLE Logistic
  fit_mle <- glm(Type ~ X, data = data, family = "binomial")
  t1_vals <- predict(fit_mle, type = "response")
  type=data$Type
  results_all <- rbind(results_all, evaluate_type_first_classifier(t1_vals, data$Type, lamda, service, costs, "MLE Logistic"))

  # 2. Bayes Gaussian
  mu1 <- mean(data$X[data$Type == 1]); mu2 <- mean(data$X[data$Type == 0])
  sd1 <- sd(data$X[data$Type == 1]); if (is.na(sd1) || sd1 == 0) sd1 <- 1e-6
  sd2 <- sd(data$X[data$Type == 0]); if (is.na(sd2) || sd2 == 0) sd2 <- 1e-6
  t1_vals <- (p1 * phi(data$X, mu1, sd1)) / (p1 * phi(data$X, mu1, sd1) + p2 * phi(data$X, mu2, sd2))
  results_all <- rbind(results_all, evaluate_type_first_classifier(t1_vals, data$Type, lamda, service, costs, "Bayes Gaussian"))
  print(results_all)
  # 3. Bayes Uniform
  a1 <- min(data$X[data$Type == 1]); b1 <- max(data$X[data$Type == 1])
  a2 <- min(data$X[data$Type == 0]); b2 <- max(data$X[data$Type == 0])
  t1_vals <- (p1 * u(data$X, a1, b1)) / (p1 * u(data$X, a1, b1) + p2 * u(data$X, a2, b2))
  results_all <- rbind(results_all, evaluate_type_first_classifier(t1_vals, data$Type, lamda, service, costs, "Bayes Uniform"))
  print(results_all)
  # 4. MoM Gaussian
  var1 <- var(data$X[data$Type == 1]); var2 <- var(data$X[data$Type == 0])
  sd1 <- sqrt(var1); if (is.na(sd1) || sd1 == 0) sd1 <- 1e-6
  sd2 <- sqrt(var2); if (is.na(sd2) || sd2 == 0) sd2 <- 1e-6
  t1_vals <- (p1 * phi(data$X, mu1, sd1)) / (p1 * phi(data$X, mu1, sd1) + p2 * phi(data$X, mu2, sd2))
  results_all <- rbind(results_all, evaluate_type_first_classifier(t1_vals, data$Type, lamda, service, costs, "MoM Gaussian"))
  print(results_all)
  # 5. MoM Uniform
  a1 <- mu1 - sqrt(3 * var1); b1 <- mu1 + sqrt(3 * var1)
  a2 <- mu2 - sqrt(3 * var2); b2 <- mu2 + sqrt(3 * var2)
  t1_vals <- (p1 * u(data$X, a1, b1)) / (p1 * u(data$X, a1, b1) + p2 * u(data$X, a2, b2))
  t1_vals <- replace_na(t1_vals,0)
  results_all <- rbind(results_all, evaluate_type_first_classifier(t1_vals, data$Type, lamda, service, costs, "MoM Uniform"))
  #print(results_all)
  
  n1 <- round(sample_size * p1)
  n2 <- sample_size - n1
  x <- c(rep(1, n1), rep(2, n2))
  sample_var <- Vectorize(function(t) if (t == 1) runif(1, 0, 3/2) else runif(1, -1, 1))
  data_test <- data.frame(Type = as.numeric(sign(1 - x) + 1), X = sample_var(x))
  
  # 6. kNN (k=10)
  t1_vals_knn10 <- get_knn_probs(data_test$X, data$X, data$Type, 10)
  results_all <- rbind(results_all, evaluate_type_first_classifier(t1_vals_knn10, data$Type, lamda, service, costs, "kNN-10"))

  # 7. kNN (k=100)
  t1_vals_knn100 <- get_knn_probs(data_test$X, data$X, data$Type, 100)
  results_all <- rbind(results_all, evaluate_type_first_classifier(t1_vals_knn100, data$Type, lamda, service, costs, "kNN-100"))

  # 8. Direct Logistic
  direct_cost <- function(par) {
    beta0 <- par[1]; beta1 <- par[2]
    decision <- ifelse((beta0 + beta1 * data$X) >= 0, 1, 2)
    ml_algo <- matrix(0, 2, 2)
    ml_algo[1,1] <- mean(decision[data$Type == 1] == 1)
    ml_algo[1,2] <- 1 - ml_algo[1,1]
    ml_algo[2,1] <- mean(decision[data$Type == 0] == 1)
    ml_algo[2,2] <- 1 - ml_algo[2,1]
    net_cost_2(ml_algo, lamda, service, costs)
  }

  par_opt <- optim(c(0.000000001, 0.99999999999999), fn = direct_cost)$par
  direct_queue <- ifelse(par_opt[1] + par_opt[2] * data$X >= 0, 1, 2)
  results_all <- rbind(results_all, evaluate_classifier(direct_queue, data$Type, lamda, service, costs, "Direct Logistic"))
}

# View final results
print(results_all)

```
















```{r}
# ---------------------------
# FIXED FULL R CODE
# ---------------------------

# Initialize result holder
results_all <- data.frame()

# Set constants
p1 <- 1/10
p2 <- 9/10
sample_size <- 10000
cost1 <- 10
cost2 <- 1
rho <- 0.7
lambda1 <- p1
lambda2 <- p2
lamda <- c(lambda1, lambda2)
service1 <- (lambda1 + lambda2) / rho
service2 <- (lambda1 + lambda2) / rho
service <- c(service1, service2)
costs <- c(cost1, cost2)

# Load required libraries
library(FNN)

# Helper functions
phi <- function(x, mu, sd) dnorm(x, mu, sd)
u <- function(x, a, b) {
  if (b - a <= 0) return(rep(0, length(x)))
  ifelse(x >= a & x <= b, 1 / (b - a), 0)
}

evaluate_classifier <- function(queue1, type, lamda, service, costs, method_name) {
  p11 <- replace_na(mean(queue1[type == 1] == 1),0)
  p21 <-replace_na(mean(queue1[type == 0] == 1),0)
  ml_algo <- matrix(c(p11, 1 - p11, p21, 1 - p21), nrow = 2, byrow = TRUE)
  priority <- priority_sequence(ml_algo, lamda, service, costs)
  wait1 <- p11*wait_k(1, ml_algo, lamda, service, costs, priority)+(1-p11)*wait_k(2, ml_algo, lamda, service, costs, priority)
  wait2 <- p21*wait_k(1, ml_algo, lamda, service, costs, priority)+(1-p21)*wait_k(2, ml_algo, lamda, service, costs, priority)

  return(data.frame(
    method = method_name,
    P11 = p11,
    P21 = p21,
    Wait1 = wait1,
    Wait2 = wait2
  ))
}

evaluate_type_first_classifier <- function(t1_vals, type, lamda, service, costs, method_name = "method") {
  if (all(is.na(t1_vals)) || length(t1_vals) == 0) {
    warning(paste("Skipping method:", method_name, "due to invalid t1_vals"))
    return(data.frame(method = method_name, P11 = NA, P21 = NA, Wait1 = NA, Wait2 = NA))
  }
 type=data$Type
  thresholds <- seq(0.000000001, 1, 0.001)
  # Here for estimating the cost function we don't use the actual type, instead we use the predicted type posteriors
  cost_fn <- function(t) {
    queue1 <- ifelse(t1_vals >= t, 1, 2)
    ml_algo <- matrix(0, 2, 2)
    ml_algo[1,1] <-sum(t1_vals*as.numeric(queue1 == 1))/sum(t1_vals)
    ml_algo[1,2] <- 1 - ml_algo[1,1]
    ml_algo[2,1] <- sum((1-t1_vals)*as.numeric(queue1 == 1))/sum(1-t1_vals)
    ml_algo[2,2] <- 1 - ml_algo[2,1]
    net_cost_2(ml_algo, lamda, service, costs)
  }

  costs_vec <- suppressWarnings(Vectorize(cost_fn)(thresholds))
  if (all(is.infinite(costs_vec))) {
    warning(paste("All costs are Inf for method:", method_name))
    return(data.frame(method = method_name, P11 = NA, P21 = NA, Wait1 = NA, Wait2 = NA))
  }

  t_opt <- thresholds[which.min(costs_vec)]
  queue1 <- ifelse(t1_vals >= t_opt, 1, 2)
  cbind(t_opt,evaluate_classifier(queue1, type, lamda, service, costs, method_name))
}

get_knn_probs <- function(test_x, train_x, train_y, k) {
  neighbors <- FNN::get.knnx(data = matrix(train_x), query = matrix(test_x), k = k)
  apply(neighbors$nn.index, 1, function(idx) mean(train_y[idx] == 1))
}

# Main loop
set.seed(1200)
for (i in c(1)) {
  n1 <- round(sample_size * p1)
  n2 <- sample_size - n1
  x <- c(rep(1, n1), rep(2, n2))
  sample_var <- Vectorize(function(t) if (t == 1) runif(1, 0, 3/2) else runif(1, -1, 1))
  data <- data.frame(Type = as.numeric(sign(1 - x) + 1), X = sample_var(x))

  # 1. MLE Logistic
  fit_mle <- glm(Type ~ X, data = data, family = "binomial")
  t1_vals <- predict(fit_mle, type = "response")
  type=data$Type
  results_all <- rbind(results_all, evaluate_type_first_classifier(t1_vals, data$Type, lamda, service, costs, "MLE Logistic"))

  # 2. Bayes Gaussian
  mu1 <- mean(data$X[data$Type == 1]); mu2 <- mean(data$X[data$Type == 0])
  sd1 <- sd(data$X[data$Type == 1]); if (is.na(sd1) || sd1 == 0) sd1 <- 1e-6
  sd2 <- sd(data$X[data$Type == 0]); if (is.na(sd2) || sd2 == 0) sd2 <- 1e-6
  t1_vals <- (p1 * phi(data$X, mu1, sd1)) / (p1 * phi(data$X, mu1, sd1) + p2 * phi(data$X, mu2, sd2))
  results_all <- rbind(results_all, evaluate_type_first_classifier(t1_vals, data$Type, lamda, service, costs, "Bayes Gaussian"))
  print(results_all)
  # 3. Bayes Uniform
  a1 <- min(data$X[data$Type == 1]); b1 <- max(data$X[data$Type == 1])
  a2 <- min(data$X[data$Type == 0]); b2 <- max(data$X[data$Type == 0])
  t1_vals <- (p1 * u(data$X, a1, b1)) / (p1 * u(data$X, a1, b1) + p2 * u(data$X, a2, b2))
  results_all <- rbind(results_all, evaluate_type_first_classifier(t1_vals, data$Type, lamda, service, costs, "Bayes Uniform"))
  print(results_all)
  # 4. MoM Gaussian
  var1 <- var(data$X[data$Type == 1]); var2 <- var(data$X[data$Type == 0])
  sd1 <- sqrt(var1); if (is.na(sd1) || sd1 == 0) sd1 <- 1e-6
  sd2 <- sqrt(var2); if (is.na(sd2) || sd2 == 0) sd2 <- 1e-6
  t1_vals <- (p1 * phi(data$X, mu1, sd1)) / (p1 * phi(data$X, mu1, sd1) + p2 * phi(data$X, mu2, sd2))
  results_all <- rbind(results_all, evaluate_type_first_classifier(t1_vals, data$Type, lamda, service, costs, "MoM Gaussian"))
  print(results_all)
  # 5. MoM Uniform
  a1 <- mu1 - sqrt(3 * var1); b1 <- mu1 + sqrt(3 * var1)
  a2 <- mu2 - sqrt(3 * var2); b2 <- mu2 + sqrt(3 * var2)
  t1_vals <- (p1 * u(data$X, a1, b1)) / (p1 * u(data$X, a1, b1) + p2 * u(data$X, a2, b2))
  t1_vals <- replace_na(t1_vals,0)
  results_all <- rbind(results_all, evaluate_type_first_classifier(t1_vals, data$Type, lamda, service, costs, "MoM Uniform"))
  #print(results_all)
  
  n1 <- round(sample_size * p1)
  n2 <- sample_size - n1
  x <- c(rep(1, n1), rep(2, n2))
  sample_var <- Vectorize(function(t) if (t == 1) runif(1, 0, 3/2) else runif(1, -1, 1))
  data_test <- data.frame(Type = as.numeric(sign(1 - x) + 1), X = sample_var(x))
  
  # 6. kNN (k=10)
  t1_vals_knn10 <- get_knn_probs(data$X, data$X, data$Type, 10)
   obj1 <- evaluate_type_first_classifier(t1_vals_knn10, data$Type, lamda, service, costs, "kNN-10")
   t_opt=obj1$t_opt
   t1_vals<- get_knn_probs(data_test$X, data$X, data$Type, 10)
   queue1 <- ifelse(t1_vals >= t_opt, 1, 2)
    type = data_test$Type
    p11 <- replace_na(mean(queue1[type == 1] == 1),0)
   p21 <-replace_na(mean(queue1[type == 0] == 1),0)
   ml_algo <- matrix(c(p11, 1 - p11, p21, 1 - p21), nrow = 2, byrow = TRUE)
  priority <- priority_sequence(ml_algo, lamda, service, costs)
  wait1 <- p11*wait_k(1, ml_algo, lamda, service, costs, priority)+(1-p11)*wait_k(2, ml_algo, lamda, service, costs, priority)
  wait2 <- p21*wait_k(1, ml_algo, lamda, service, costs, priority)+(1-p21)*wait_k(2, ml_algo, lamda, service, costs, priority)
    results_all <- rbind(results_all, data.frame(t_opt,
    method = "kNN-10",
    P11 = p11,
    P21 = p21,
    Wait1 = wait1,
    Wait2 = wait2
  ))
  
  # 7. kNN (k=100)
 t1_vals_knn100 <- get_knn_probs(data$X, data$X, data$Type, 100)
   obj1 <- evaluate_type_first_classifier(t1_vals_knn100, data$Type, lamda, service, costs, "kNN-100")
   t_opt=obj1$t_opt
   t1_vals<- get_knn_probs(data_test$X, data$X, data$Type, 100)
   queue1 <- ifelse(t1_vals >= t_opt, 1, 2)
    type = data_test$Type
    p11 <- replace_na(mean(queue1[type == 1] == 1),0)
   p21 <-replace_na(mean(queue1[type == 0] == 1),0)
   ml_algo <- matrix(c(p11, 1 - p11, p21, 1 - p21), nrow = 2, byrow = TRUE)
  priority <- priority_sequence(ml_algo, lamda, service, costs)
  wait1 <- p11*wait_k(1, ml_algo, lamda, service, costs, priority)+(1-p11)*wait_k(2, ml_algo, lamda, service, costs, priority)
  wait2 <- p21*wait_k(1, ml_algo, lamda, service, costs, priority)+(1-p21)*wait_k(2, ml_algo, lamda, service, costs, priority)
    results_all <- rbind(results_all, data.frame(t_opt,
    method = "kNN-100",
    P11 = p11,
    P21 = p21,
    Wait1 = wait1,
    Wait2 = wait2
  ))
  # 8. Direct Logistic
  direct_cost <- function(par) {
    beta0 <- par[1]; beta1 <- par[2]
    decision <- ifelse((beta0 + beta1 * data$X) >= 0, 1, 2)
    ml_algo <- matrix(0, 2, 2)
    ml_algo[1,1] <- mean(decision[data$Type == 1] == 1)
    ml_algo[1,2] <- 1 - ml_algo[1,1]
    ml_algo[2,1] <- mean(decision[data$Type == 0] == 1)
    ml_algo[2,2] <- 1 - ml_algo[2,1]
    net_cost_2(ml_algo, lamda, service, costs)
  }

  par_opt <- optim(c(0.000000001, 0.99999999999999), fn = direct_cost)$par
  direct_queue <- ifelse(par_opt[1] + par_opt[2] * data$X >= 0, 1, 2)
  results_all <- rbind(results_all, cbind(t_opt=0.5,evaluate_classifier(direct_queue, data$Type, lamda, service, costs, "Direct Logistic")))
}

# View final results
print(results_all)

```























```{r}
mean(pt_11)
#sd(pt_11)
se=sd(pt_11)/sqrt(25)
#se
1.96*se
#lower=mean(pt_11)+qnorm(0.025)*se
#upper=mean(pt_11)+qnorm(0.975)*se
#lower
#upper
```



```{r}
mean(pt_21)
#sd(pt_11)
se=sd(pt_21)/sqrt(25)
1.96*se
#lower=mean(pt_21)+qnorm(0.025)*se
#upper=mean(pt_21)+qnorm(0.975)*se
#lower
#upper
```


```{r}
mean(pd_11)
#sd(pt_11)
se=sd(pd_11)/sqrt(25)
1.96*se
lower=mean(pd_11)+qnorm(0.025)*se
upper=mean(pd_11)+qnorm(0.975)*se
#lower
#upper
```

```{r}
mean(pd_21)
#sd(pt_11)
se=sd(pd_21)/sqrt(25)
1.96*se
lower=mean(pd_21)+qnorm(0.025)*se
upper=mean(pd_21)+qnorm(0.975)*se
#lower
#upper
```






































### This assumes the type first is a logistic regression classifier obtained via MLE estimates

##### Running the Experiment 25 times ######


```{r}
source("../utils/cost_functions.R")
source("../utils/header.R")
library(distr)
```



```{r}
cost1=10
cost2=1
rho=0.7
p1=1/10
p2=9/10
lambda1=p1
lambda2=p2
service1=(lambda1+lambda2)/rho
service2=(lambda1+lambda2)/rho
service1
service2
ml_algo=rbind(c(1,0),c(0,1))
lamda=c(lambda1,lambda2)
service=c(service1,service2)
costs=c(cost1,cost2)
sample_size=10000
pt_11=vector()
pt_21=vector()
pd_11=vector()
pd_21=vector()
for(i in 1:25){
myMix <- UnivarMixingDistribution(DiscreteDistribution(1), 
                                DiscreteDistribution(2),
                                  mixCoeff=c(p1,p2))
rmyMix <- r(myMix)
x <- rmyMix(sample_size)
#hist(x, col="grey", main="")
sample_var=function(x){
  if(x==1){
    return(runif(1,0,3/2))
  }else if(x==2)
    {
    return(runif(1,-1,1))
  }
}
sample_var=Vectorize(sample_var)
data=cbind(Type=x,X=sample_var(x))
data=as.data.frame(data)
data$Type=as.numeric(sign(1-data$Type)+1)
fit=glm(Type~X,data,family="binomial")
classifier_predictions=fit$fitted.values
estimated_cost_thresh=function(t){
  p11=sum(classifier_predictions*0.5*(1+sign(classifier_predictions-t)))/sum(classifier_predictions)
  p21=sum((1-classifier_predictions)*0.5*(1+sign(classifier_predictions-t)))/sum(1-classifier_predictions)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
estimated_cost_thresh=Vectorize(estimated_cost_thresh)
thresholds=seq(0,1,0.001)
min(estimated_cost_thresh(thresholds))
t=thresholds[which.min(estimated_cost_thresh(thresholds))]
x_c=(qlogis(t)-fit$coefficients[1])/fit$coefficients[2]
p11=1-2*x_c/3
p21=1-(1+x_c)/2
pt_11[i]=p11
pt_21[i]=p21
estimated_cost_direct=function(par){
  beta_0=par[1]
  beta_1=par[2]
  p11=sum(data$Type*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(data$Type)
  p21=sum((1-data$Type)*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(1-data$Type)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)
par=optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)$par
x_c=-par[1]/par[2]
p11=1-2*x_c/3
p21=1-(1+x_c)/2
pd_11[i]=p11
pd_21[i]=p21
#print(i)
}
mean(pt_11)
#sd(pt_11)
se=sd(pt_11)/sqrt(25)
#se
1.96*se
#lower=mean(pt_11)+qnorm(0.025)*se
#upper=mean(pt_11)+qnorm(0.975)*se
#lower
#upper
mean(pt_21)
#sd(pt_11)
se=sd(pt_21)/sqrt(25)
1.96*se
#lower=mean(pt_21)+qnorm(0.025)*se
#upper=mean(pt_21)+qnorm(0.975)*se
#lower
#upper
mean(pd_11)
#sd(pt_11)
se=sd(pd_11)/sqrt(25)
1.96*se
lower=mean(pd_11)+qnorm(0.025)*se
upper=mean(pd_11)+qnorm(0.975)*se
#lower
#upper
mean(pd_21)
#sd(pt_11)
se=sd(pd_21)/sqrt(25)
1.96*se
lower=mean(pd_21)+qnorm(0.025)*se
upper=mean(pd_21)+qnorm(0.975)*se
#lower
#upper
ml_algo_type_first=rbind(c(mean(pt_11),mean(1-pt_11)),c(mean(pt_21),mean(1-pt_21)))
ml_algo_type_first
ml_algo_direct=rbind(c(mean(pd_11),mean(1-pd_11)),c(mean(pd_21),mean(1-pd_21)))
ml_algo_direct
costs=c(cost1,cost2)
net_cost_2(ml_algo=ml_algo_type_first,lamda,service,costs)
net_cost_2(ml_algo=ml_algo_direct,lamda,service,costs)

(net_cost_2(ml_algo=ml_algo_type_first,lamda,service,costs)-net_cost_2(ml_algo=ml_algo_direct,lamda,service,costs))/net_cost_2(ml_algo=ml_algo_direct,lamda,service,costs)
```

#Next, we try some other classifiers. 

#First, we try a Naive Bayes Classifier



```{r}
cost1=10
cost2=1
rho=0.7
p1=1/10
p2=9/10
lambda1=p1
lambda2=p2
service1=(lambda1+lambda2)/rho
service2=(lambda1+lambda2)/rho
service1
service2
ml_algo=rbind(c(1,0),c(0,1))
lamda=c(lambda1,lambda2)
service=c(service1,service2)
costs=c(cost1,cost2)
sample_size=10000
pt_11=vector()
pt_21=vector()
pd_11=vector()
pd_21=vector()
for(i in 1:25){
myMix <- UnivarMixingDistribution(DiscreteDistribution(1), 
                                DiscreteDistribution(2),
                                  mixCoeff=c(p1,p2))
rmyMix <- r(myMix)
x <- rmyMix(sample_size)
#hist(x, col="grey", main="")
sample_var=function(x){
  if(x==1){
    return(runif(1,0,3/2))
  }else if(x==2)
    {
    return(runif(1,-1,1))
  }
}
sample_var=Vectorize(sample_var)
data=cbind(Type=x,X=sample_var(x))
data=as.data.frame(data)
data$Type=as.numeric(sign(1-data$Type)+1)
library(e1071)
fit = naiveBayes(Type ~ X, data = data)
preds = predict(fit, newdata = data, type = "raw")
classifier_predictions=preds[,2]
estimated_cost_thresh=function(t){
  p11=sum(classifier_predictions*0.5*(1+sign(classifier_predictions-t)))/sum(classifier_predictions)
  p21=sum((1-classifier_predictions)*0.5*(1+sign(classifier_predictions-t)))/sum(1-classifier_predictions)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
estimated_cost_thresh=Vectorize(estimated_cost_thresh)
thresholds=seq(0,1,0.001)
min(estimated_cost_thresh(thresholds))
t=thresholds[which.min(estimated_cost_thresh(thresholds))]
#x_c=(qlogis(t)-fit$coefficients[1])/fit$coefficients[2]
#p11=1-2*x_c/3
#p21=1-(1+x_c)/2
pred_queue=0.5*(1+sign(classifier_predictions-t))
pt_11[i]=sum(data$Type*pred_queue)/sum(data$Type)
pt_21[i]=sum((1-data$Type)*pred_queue)/sum(1-data$Type)
estimated_cost_direct=function(par){
  beta_0=par[1]
  beta_1=par[2]
  p11=sum(data$Type*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(data$Type)
  p21=sum((1-data$Type)*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(1-data$Type)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
fit2=glm(Type~X,data,family="binomial")
#optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)
par=optim(par=c(fit2$coefficients[1],fit2$coefficients[2]),fn=estimated_cost_direct)$par
x_c=-par[1]/par[2]
p11=1-2*x_c/3
p21=1-(1+x_c)/2
pd_11[i]=p11
pd_21[i]=p21
#print(i)
}
mean(pt_11)
#sd(pt_11)
se=sd(pt_11)/sqrt(25)
#se
1.96*se
#lower=mean(pt_11)+qnorm(0.025)*se
#upper=mean(pt_11)+qnorm(0.975)*se
#lower
#upper
mean(pt_21)
#sd(pt_11)
se=sd(pt_21)/sqrt(25)
1.96*se
#lower=mean(pt_21)+qnorm(0.025)*se
#upper=mean(pt_21)+qnorm(0.975)*se
#lower
#upper
mean(pd_11)
#sd(pt_11)
se=sd(pd_11)/sqrt(25)
1.96*se
lower=mean(pd_11)+qnorm(0.025)*se
upper=mean(pd_11)+qnorm(0.975)*se
#lower
#upper
mean(pd_21)
#sd(pt_11)
se=sd(pd_21)/sqrt(25)
1.96*se
lower=mean(pd_21)+qnorm(0.025)*se
upper=mean(pd_21)+qnorm(0.975)*se
#lower
#upper
ml_algo_type_first=rbind(c(mean(pt_11),mean(1-pt_11)),c(mean(pt_21),mean(1-pt_21)))
ml_algo_type_first
ml_algo_direct=rbind(c(mean(pd_11),mean(1-pd_11)),c(mean(pd_21),mean(1-pd_21)))
ml_algo_direct
costs=c(cost1,cost2)
net_cost_2(ml_algo=ml_algo_type_first,lamda,service,costs)
net_cost_2(ml_algo=ml_algo_direct,lamda,service,costs)

(net_cost_2(ml_algo=ml_algo_type_first,lamda,service,costs)-net_cost_2(ml_algo=ml_algo_direct,lamda,service,costs))/net_cost_2(ml_algo=ml_algo_direct,lamda,service,costs)

```


# non-MLE classifier—specifically a Bayesian Gaussian Naive Bayes classifier with conjugate prior shrinkage on the mean.

```{r}
cost1=10
cost2=1
rho=0.7
p1=1/10
p2=9/10
lambda1=p1
lambda2=p2
service1=(lambda1+lambda2)/rho
service2=(lambda1+lambda2)/rho
service1
service2
ml_algo=rbind(c(1,0),c(0,1))
lamda=c(lambda1,lambda2)
service=c(service1,service2)
costs=c(cost1,cost2)
sample_size=10000
mu0_prior = 0
tau2 = 0.1 # Prior variance (adjustable)
pt_11=vector()
pt_21=vector()
pd_11=vector()
pd_21=vector()
for(i in 1:25){
myMix <- UnivarMixingDistribution(DiscreteDistribution(1), 
                                DiscreteDistribution(2),
                                  mixCoeff=c(p1,p2))
rmyMix <- r(myMix)
x <- rmyMix(sample_size)
#hist(x, col="grey", main="")
sample_var=function(x){
  if(x==1){
    return(runif(1,0,3/2))
  }else if(x==2)
    {
    return(runif(1,-1,1))
  }
}
sample_var=Vectorize(sample_var)
data=cbind(Type=x,X=sample_var(x))
data=as.data.frame(data)
data$Type=as.numeric(sign(1-data$Type)+1)
library(e1071)
  # Estimate class priors
  class_counts <- table(data$Type)
  n0 <- class_counts["0"]
  n1 <- class_counts["1"]
  prior0 <- n0 / sample_size
  prior1 <- n1 / sample_size
  
  # Estimate posterior means and variances (Naive Bayes)
  data0 <- data[data$Type == 0, "X"]
  data1 <- data[data$Type == 1, "X"]
  
  # MLE estimates
  xbar0 <- mean(data0)
  xbar1 <- mean(data1)
  s20 <- var(data0)
  s21 <- var(data1)
  
  # Bayesian posterior means
  mu0_post <- (tau2 * xbar0 + s20 * mu0_prior / n0) / (tau2 + s20 / n0)
  mu1_post <- (tau2 * xbar1 + s21 * mu0_prior / n1) / (tau2 + s21 / n1)
  
  # Gaussian density function
  gaussian_pdf <- function(x, mu, sigma2) {
    return(dnorm(x, mean = mu, sd = sqrt(sigma2)))
  }
  
  # Compute posterior P(Y = 1 | X) using Bayes rule
  pred_probs <- mapply(function(xi) {
    num1 <- prior1 * gaussian_pdf(xi, mu1_post, s21)
    num0 <- prior0 * gaussian_pdf(xi, mu0_post, s20)
    return(num1 / (num1 + num0))
  }, data$X)
  
  # These are your non-MLE classifier predictions (posterior probs)
  classifier_predictions <- pred_probs
estimated_cost_thresh=function(t){
  p11=sum(classifier_predictions*0.5*(1+sign(classifier_predictions-t)))/sum(classifier_predictions)
  p21=sum((1-classifier_predictions)*0.5*(1+sign(classifier_predictions-t)))/sum(1-classifier_predictions)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
estimated_cost_thresh=Vectorize(estimated_cost_thresh)
thresholds=seq(0,1,0.001)
min(estimated_cost_thresh(thresholds))
t=thresholds[which.min(estimated_cost_thresh(thresholds))]
#x_c=(qlogis(t)-fit$coefficients[1])/fit$coefficients[2]
#p11=1-2*x_c/3
#p21=1-(1+x_c)/2
pred_queue=0.5*(1+sign(classifier_predictions-t))
pt_11[i]=sum(data$Type*pred_queue)/sum(data$Type)
pt_21[i]=sum((1-data$Type)*pred_queue)/sum(1-data$Type)
estimated_cost_direct=function(par){
  beta_0=par[1]
  beta_1=par[2]
  p11=sum(data$Type*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(data$Type)
  p21=sum((1-data$Type)*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(1-data$Type)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
fit2=glm(Type~X,data,family="binomial")
#optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)
par=optim(par=c(fit2$coefficients[1],fit2$coefficients[2]),fn=estimated_cost_direct)$par
x_c=-par[1]/par[2]
p11=1-2*x_c/3
p21=1-(1+x_c)/2
pd_11[i]=p11
pd_21[i]=p21
#print(i)
}
mean(pt_11)
#sd(pt_11)
se=sd(pt_11)/sqrt(25)
#se
1.96*se
#lower=mean(pt_11)+qnorm(0.025)*se
#upper=mean(pt_11)+qnorm(0.975)*se
#lower
#upper
mean(pt_21)
#sd(pt_11)
se=sd(pt_21)/sqrt(25)
1.96*se
#lower=mean(pt_21)+qnorm(0.025)*se
#upper=mean(pt_21)+qnorm(0.975)*se
#lower
#upper
mean(pd_11)
#sd(pt_11)
se=sd(pd_11)/sqrt(25)
1.96*se
lower=mean(pd_11)+qnorm(0.025)*se
upper=mean(pd_11)+qnorm(0.975)*se
#lower
#upper
mean(pd_21)
#sd(pt_11)
se=sd(pd_21)/sqrt(25)
1.96*se
lower=mean(pd_21)+qnorm(0.025)*se
upper=mean(pd_21)+qnorm(0.975)*se
#lower
#upper
ml_algo_type_first=rbind(c(mean(pt_11),mean(1-pt_11)),c(mean(pt_21),mean(1-pt_21)))
ml_algo_type_first
ml_algo_direct=rbind(c(mean(pd_11),mean(1-pd_11)),c(mean(pd_21),mean(1-pd_21)))
ml_algo_direct
costs=c(cost1,cost2)
net_cost_2(ml_algo=ml_algo_type_first,lamda,service,costs)
net_cost_2(ml_algo=ml_algo_direct,lamda,service,costs)

(net_cost_2(ml_algo=ml_algo_type_first,lamda,service,costs)-net_cost_2(ml_algo=ml_algo_direct,lamda,service,costs))/net_cost_2(ml_algo=ml_algo_direct,lamda,service,costs)
```






```{r}
cost1=10
cost2=1
rho=0.7
p1=1/10
p2=9/10
lambda1=p1
lambda2=p2
service1=(lambda1+lambda2)/rho
service2=(lambda1+lambda2)/rho
service1
service2
ml_algo=rbind(c(1,0),c(0,1))
lamda=c(lambda1,lambda2)
service=c(service1,service2)
costs=c(cost1,cost2)
sample_size=10000
mu0_prior = 0
tau2 = 0.1 # Prior variance (adjustable)
pt_11=vector()
pt_21=vector()
pd_11=vector()
pd_21=vector()
for(i in 1:25){
myMix <- UnivarMixingDistribution(DiscreteDistribution(1), 
                                DiscreteDistribution(2),
                                  mixCoeff=c(p1,p2))
rmyMix <- r(myMix)
x <- rmyMix(sample_size)
#hist(x, col="grey", main="")
sample_var=function(x){
  if(x==1){
    return(runif(1,0,3/2))
  }else if(x==2)
    {
    return(runif(1,-1,1))
  }
}
sample_var=Vectorize(sample_var)
data=cbind(Type=x,X=sample_var(x))
data=as.data.frame(data)
data$Type=as.numeric(sign(1-data$Type)+1)
library(e1071)
  # Estimate class priors
  class_counts <- table(data$Type)
  n0 <- class_counts["0"]
  n1 <- class_counts["1"]
  prior0 <- n0 / sample_size
  prior1 <- n1 / sample_size
  
  # Estimate posterior means and variances (Naive Bayes)
  data0 <- data[data$Type == 0, "X"]
  data1 <- data[data$Type == 1, "X"]
  
  # MLE estimates
  xbar0 <- mean(data0)
  xbar1 <- mean(data1)
  s20 <- var(data0)
  s21 <- var(data1)
  
  # Bayesian posterior means
  mu0_post <- (tau2 * xbar0 + s20 * mu0_prior / n0) / (tau2 + s20 / n0)
  mu1_post <- (tau2 * xbar1 + s21 * mu0_prior / n1) / (tau2 + s21 / n1)
  
  # Uniform density function
estimate_uniform_mom <- function(x) {
  xbar <- mean(x)
  s2 <- var(x)
  delta <- sqrt(3 * s2)
  a <- xbar - delta
  b <- xbar + delta
  return(c(a = a, b = b))
}

# Estimate parameters
uniform0 <- estimate_uniform_mom(data0)
uniform1 <- estimate_uniform_mom(data1)

# Uniform likelihood function
uniform_likelihood <- function(x, a, b) {
  ifelse(x >= a & x <= b, 1 / (b - a), 0)
}

# Posterior probabilities under uniform model
posterior_probs_uniform <- mapply(function(xi) {
  num1 <- prior1 * uniform_likelihood(xi, uniform1["a"], uniform1["b"])
  num0 <- prior0 * uniform_likelihood(xi, uniform0["a"], uniform0["b"])
  denom <- num0 + num1
  if (denom == 0) return(NA)  # outside support of both
  return(num1 / denom)
}, data$X)

classifier_predictions <- posterior_probs_uniform
classifier_predictions <- replace_na(classifier_predictions,0)
estimated_cost_thresh=function(t){
  p11=sum(classifier_predictions*0.5*(1+sign(classifier_predictions-t)))/sum(classifier_predictions)
  p21=sum((1-classifier_predictions)*0.5*(1+sign(classifier_predictions-t)))/sum(1-classifier_predictions)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
estimated_cost_thresh=Vectorize(estimated_cost_thresh)
thresholds=seq(0,1,0.001)
min(estimated_cost_thresh(thresholds))
t=thresholds[which.min(estimated_cost_thresh(thresholds))]
#x_c=(qlogis(t)-fit$coefficients[1])/fit$coefficients[2]
#p11=1-2*x_c/3
#p21=1-(1+x_c)/2
pred_queue=0.5*(1+sign(classifier_predictions-t))
pt_11[i]=sum(data$Type*pred_queue)/sum(data$Type)
pt_21[i]=sum((1-data$Type)*pred_queue)/sum(1-data$Type)
estimated_cost_direct=function(par){
  beta_0=par[1]
  beta_1=par[2]
  p11=sum(data$Type*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(data$Type)
  p21=sum((1-data$Type)*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(1-data$Type)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
fit2=glm(Type~X,data,family="binomial")
#optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)
par=optim(par=c(fit2$coefficients[1],fit2$coefficients[2]),fn=estimated_cost_direct)$par
x_c=-par[1]/par[2]
p11=1-2*x_c/3
p21=1-(1+x_c)/2
pd_11[i]=p11
pd_21[i]=p21
#print(i)
}
mean(pt_11)
#sd(pt_11)
se=sd(pt_11)/sqrt(25)
#se
1.96*se
#lower=mean(pt_11)+qnorm(0.025)*se
#upper=mean(pt_11)+qnorm(0.975)*se
#lower
#upper
mean(pt_21)
#sd(pt_11)
se=sd(pt_21)/sqrt(25)
1.96*se
#lower=mean(pt_21)+qnorm(0.025)*se
#upper=mean(pt_21)+qnorm(0.975)*se
#lower
#upper
mean(pd_11)
#sd(pt_11)
se=sd(pd_11)/sqrt(25)
1.96*se
lower=mean(pd_11)+qnorm(0.025)*se
upper=mean(pd_11)+qnorm(0.975)*se
#lower
#upper
mean(pd_21)
#sd(pt_11)
se=sd(pd_21)/sqrt(25)
1.96*se
lower=mean(pd_21)+qnorm(0.025)*se
upper=mean(pd_21)+qnorm(0.975)*se
#lower
#upper
ml_algo_type_first=rbind(c(mean(pt_11),mean(1-pt_11)),c(mean(pt_21),mean(1-pt_21)))
ml_algo_type_first
ml_algo_direct=rbind(c(mean(pd_11),mean(1-pd_11)),c(mean(pd_21),mean(1-pd_21)))
ml_algo_direct
costs=c(cost1,cost2)
net_cost_2(ml_algo=ml_algo_type_first,lamda,service,costs)
net_cost_2(ml_algo=ml_algo_direct,lamda,service,costs)

(net_cost_2(ml_algo=ml_algo_type_first,lamda,service,costs)-net_cost_2(ml_algo=ml_algo_direct,lamda,service,costs))/net_cost_2(ml_algo=ml_algo_direct,lamda,service,costs)
```






















































```{r}
cost1=10
cost2=1
rho=0.7
p1=1/10
p2=9/10
lambda1=p1
lambda2=p2
service1=(lambda1+lambda2)/rho
service2=(lambda1+lambda2)/rho
service1
service2
ml_algo=rbind(c(1,0),c(0,1))
lamda=c(lambda1,lambda2)
service=c(service1,service2)
costs=c(cost1,cost2)
sample_size=10000
```

```{r}
pt_11=vector()
pt_21=vector()
pd_11=vector()
pd_21=vector()
for(i in 1:25){
myMix <- UnivarMixingDistribution(DiscreteDistribution(1), 
                                DiscreteDistribution(2),
                                  mixCoeff=c(p1,p2))
rmyMix <- r(myMix)
x <- rmyMix(sample_size)
#hist(x, col="grey", main="")
sample_var=function(x){
  if(x==1){
    return(runif(1,0,3/2))
  }else if(x==2)
    {
    return(runif(1,-1,1))
  }
}
sample_var=Vectorize(sample_var)
data=cbind(Type=x,X=sample_var(x))
data=as.data.frame(data)
data$Type=as.numeric(sign(1-data$Type)+1)
fit=glm(Type~X,data,family="binomial")
classifier_predictions=fit$fitted.values
estimated_cost_thresh=function(t){
  p11=sum(classifier_predictions*0.5*(1+sign(classifier_predictions-t)))/sum(classifier_predictions)
  p21=sum((1-classifier_predictions)*0.5*(1+sign(classifier_predictions-t)))/sum(1-classifier_predictions)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
estimated_cost_thresh=Vectorize(estimated_cost_thresh)
thresholds=seq(0,1,0.001)
min(estimated_cost_thresh(thresholds))
t=thresholds[which.min(estimated_cost_thresh(thresholds))]
x_c=(qlogis(t)-fit$coefficients[1])/fit$coefficients[2]
p11=1-2*x_c/3
p21=1-(1+x_c)/2
pt_11[i]=p11
pt_21[i]=p21
estimated_cost_direct=function(par){
  beta_0=par[1]
  beta_1=par[2]
  p11=sum(data$Type*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(data$Type)
  p21=sum((1-data$Type)*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(1-data$Type)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)
par=optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)$par
x_c=-par[1]/par[2]
p11=1-2*x_c/3
p21=1-(1+x_c)/2
pd_11[i]=p11
pd_21[i]=p21
#print(i)
}
```



```{r}
mean(pt_11)
#sd(pt_11)
se=sd(pt_11)/sqrt(25)
#se
1.96*se
#lower=mean(pt_11)+qnorm(0.025)*se
#upper=mean(pt_11)+qnorm(0.975)*se
#lower
#upper
```



```{r}
mean(pt_21)
#sd(pt_11)
se=sd(pt_21)/sqrt(25)
1.96*se
#lower=mean(pt_21)+qnorm(0.025)*se
#upper=mean(pt_21)+qnorm(0.975)*se
#lower
#upper
```


```{r}
mean(pd_11)
#sd(pt_11)
se=sd(pd_11)/sqrt(25)
1.96*se
lower=mean(pd_11)+qnorm(0.025)*se
upper=mean(pd_11)+qnorm(0.975)*se
#lower
#upper
```

```{r}
mean(pd_21)
#sd(pt_11)
se=sd(pd_21)/sqrt(25)
1.96*se
lower=mean(pd_21)+qnorm(0.025)*se
upper=mean(pd_21)+qnorm(0.975)*se
#lower
#upper
```




```{r}
source("../utils/cost_functions.R")
source("../utils/header.R")
library(distr)
```


```{r}
cost1=10
cost2=1
rho=0.7
p1=1/10
p2=9/10
lambda1=p1
lambda2=p2
service1=(lambda1+lambda2)/rho
service2=(lambda1+lambda2)/rho
service1
service2
ml_algo=rbind(c(1,0),c(0,1))
lamda=c(lambda1,lambda2)
service=c(service1,service2)
costs=c(cost1,cost2)
sample_size=100000
```

```{r}
pt_11=vector()
pt_21=vector()
pd_11=vector()
pd_21=vector()
for(i in 1:25){
myMix <- UnivarMixingDistribution(DiscreteDistribution(1), 
                                DiscreteDistribution(2),
                                  mixCoeff=c(p1,p2))
rmyMix <- r(myMix)
x <- rmyMix(sample_size)
#hist(x, col="grey", main="")
sample_var=function(x){
  if(x==1){
    return(runif(1,0,3/2))
  }else if(x==2)
    {
    return(runif(1,-1,1))
  }
}
sample_var=Vectorize(sample_var)
data=cbind(Type=x,X=sample_var(x))
data=as.data.frame(data)
data$Type=as.numeric(sign(1-data$Type)+1)
fit=glm(Type~X,data,family="binomial")
classifier_predictions=fit$fitted.values
estimated_cost_thresh=function(t){
  p11=sum(classifier_predictions*0.5*(1+sign(classifier_predictions-t)))/sum(classifier_predictions)
  p21=sum((1-classifier_predictions)*0.5*(1+sign(classifier_predictions-t)))/sum(1-classifier_predictions)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
estimated_cost_thresh=Vectorize(estimated_cost_thresh)
thresholds=seq(0,1,0.001)
min(estimated_cost_thresh(thresholds))
t=thresholds[which.min(estimated_cost_thresh(thresholds))]
x_c=(qlogis(t)-fit$coefficients[1])/fit$coefficients[2]
p11=1-2*x_c/3
p21=1-(1+x_c)/2
pt_11[i]=p11
pt_21[i]=p21
estimated_cost_direct=function(par){
  beta_0=par[1]
  beta_1=par[2]
  p11=sum(data$Type*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(data$Type)
  p21=sum((1-data$Type)*0.5*(1+sign(beta_0+beta_1*data$X)))/sum(1-data$Type)
  p12=1-p11
  p22=1-p21
  ml_algo=rbind(c(p11,p12),c(p21,p22))
  return(net_cost_2(ml_algo,lamda,service,costs))
}
optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)
par=optim(par=c(fit$coefficients[1],fit$coefficients[2]),fn=estimated_cost_direct)$par
x_c=-par[1]/par[2]
p11=1-2*x_c/3
p21=1-(1+x_c)/2
pd_11[i]=p11
pd_21[i]=p21
#print(i)
}
```


```{r}
mean(pt_11)
#sd(pt_11)
se=sd(pt_11)/sqrt(10)
#se
1.96*se
#lower=mean(pt_11)+qnorm(0.025)*se
#upper=mean(pt_11)+qnorm(0.975)*se
#lower
#upper
```



```{r}
mean(pt_21)
#sd(pt_11)
se=sd(pt_21)/sqrt(10)
1.96*se
#lower=mean(pt_21)+qnorm(0.025)*se
#upper=mean(pt_21)+qnorm(0.975)*se
#lower
#upper
```


```{r}
mean(pd_11)
#sd(pt_11)
se=sd(pd_11)/sqrt(10)
1.96*se
lower=mean(pd_11)+qnorm(0.025)*se
upper=mean(pd_11)+qnorm(0.975)*se
#lower
#upper
```

```{r}
mean(pd_21)
#sd(pt_11)
se=sd(pd_21)/sqrt(10)
1.96*se
lower=mean(pd_21)+qnorm(0.025)*se
upper=mean(pd_21)+qnorm(0.975)*se
#lower
#upper
```





